Eliminating prior-bias from sparse-projection tomographic reconstructions

### 2020-06-11 paper/tci.tex
Modified Fig.16. (zoomed sprouts)

  \item Next, for each $j$,  project $X^j$  onto $\boldsymbol{V_\text{low}^j}$. Let this projection be denoted by $P^j$. To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e. are similar to the template reconstructions). The rest, i.e. new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
  \end{enumerate}
%\vspace{-0.1cm}
\item To remove all reconstruction method dependent false positives, we compute $\min_{j}(|X^j(x,y,z) - P^j(x,y,z)|)$. (The intuition for using the `min' is provided in the paragraph immediately following step 6 of this procedure.)
\item Finally, the weight to prior for each voxel coordinate $(x,y,z)$ is given by
  \begin{equation} 
    \boldsymbol{W_v}(x,y,z) = (1+k(\min_{j}|X^j(x,y,z) - P^j(x,y,z)|))^{-1}.
  \end{equation}
\label{eq:weightsEq}
\end{enumerate}
\vspace{0.01mm}
Note that here $\boldsymbol{W_v}(x,y,z)$ represents the weight to the prior in the $(x,y,z)^{th}$ voxel. $\boldsymbol{W_v}(x,y,z)$ must be
low whenever the preliminary test reconstruction $X^j(x,y,z)$ is different from its projection $P^j(x,y,z)$ onto the prior eigenspace, for \emph{every} method $j \in \{1,...,M\}$. This is
because it is unlikely that \emph{every} algorithm would produce a significant artefact at a voxel, and hence we hypothesize that the large difference has arisen due to genuine structural changes. The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$ and hence it depends on the size of the new regions we want to detect.  
%It must be chosen empirically based on the reconstruction of one of the template
%volumes. 
We found that our final reconstruction results obtained by
solving Eq.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
%-------------------------------------------
\subsubsection{\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights}}

@@

\begin{figure}[!h]
\centering
\subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_marked.png}}\hfill
\subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_marked.png}}\hfill
\subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_marked.png}}\hfill
\subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods (a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
\label{fig:sprouts_zoomed_3D_results}
\end{figure}

>>>>

  \item Next, for each $j$,  project $X^j$  onto $\boldsymbol{V_\text{low}^j}$. Let this projection be denoted by $P^j$. To reiterate, this captures those parts of the test volume that lie in the subspace $\boldsymbol{V_\text{low}^j}$ (i.e. are similar to the template reconstructions). The rest, i.e. new changes and their reconstruction method-dependent-artefacts, are not captured by this projection and need to be eliminated.
  \end{enumerate}
%\vspace{-0.1cm}
\item To remove all reconstruction method dependent false positives, we compute $\min_{j}(|X^j(x,y,z) - P^j(x,y,z)|)$. (The intuition for using the `min' is provided in the paragraph immediately following step 6 of this procedure.)
\item Finally, the weight to prior for each voxel coordinate $(x,y,z)$ is given by
  \begin{equation} 
    \boldsymbol{W_v}(x,y,z) = (1+k(\min_{j}|X^j(x,y,z) - P^j(x,y,z)|))^{-1}.
    \label{eq:weightsEq}
  \end{equation}
\end{enumerate}
\vspace{0.01mm}
Note that here $\boldsymbol{W_v}(x,y,z)$ represents the weight to the prior in the $(x,y,z)^{th}$ voxel. $\boldsymbol{W_v}(x,y,z)$ must be
low whenever the preliminary test reconstruction $X^j(x,y,z)$ is different from its projection $P^j(x,y,z)$ onto the prior eigenspace, for \emph{every} method $j \in \{1,...,M\}$. This is
because it is unlikely that \emph{every} algorithm would produce a significant artefact at a voxel, and hence we hypothesize that the large difference has arisen due to genuine structural changes. The parameter $k$ decides the sensitivity of the weights to the difference $|X^j(x,y,z) - P^j(x,y,z)|$ and hence it depends on the size of the new regions we want to detect.  
%It must be chosen empirically based on the reconstruction of one of the template
%volumes. 
We found that our final reconstruction results obtained by
solving Eq.~\ref{eq:selective_prior} were robust over a wide range of $k$ values, as discussed in Sec.~\ref{sec:discussion}.
%-------------------------------------------
\subsubsection{\textbf{Motivation for the use of multiple types of eigenspaces for the computation of weights}}

@@

\begin{figure}[!h]
  \centering
  \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_croppedBig.png}}\hfill
    \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_croppedBig.png}}\hfill
      \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_croppedBig.png}}\hfill
        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_croppedBig.png}}\hfill
        \subcaptionbox*{}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_croppedBig.png}}\hfill
          \subcaptionbox{Test}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/input_marked.png}}\hfill
            \subcaptionbox{FDK, no prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/FDK_marked.png}}\hfill
              \subcaptionbox{l1-ls}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/CS_marked.png}}\hfill
                \subcaptionbox{\mbox{Unselective}\\prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/pca_marked.png}}\hfill
\subcaptionbox{Selective\\ prior}{\includegraphics[width=0.19\columnwidth]{../images/sprouts/zoomed/weighted_prior_marked.png}}
\caption{Zoomed-in portion $(41 \times 36)$ containing the RoI of Fig.~\ref{fig:sprouts_3D_results} for various methods. The images of the bottom row are the same as repective images of the top row, with regions marked additionally. (a) the test showing 3 distinct structures (in red here) (b) 3 structures recovered with poor contrast, (c) structures indistinguishable, (d) only two strong structures seen and (e) there is a hint of a third structure too with better contrast.}
\label{fig:sprouts_zoomed_3D_results}
\end{figure}
